Tactics and Marks in Banach Mazur Games

### 2018-02-21 postdoctoral/k-markov-tactic-banach-mazur.tex
add work towards (k+2)-mark to (k+2)-tactic

@@

  \begin{observation}
    When \(\mb P=\{(U,x):U\in T(X)\setminus\{\emptyset\},x\in U\}\)
    is ordered by \((U,x)\geq(V,y)\) whenever \(x\in V\subseteq U\)
    and \(W=\{\<U(n),x(n)\>_{n<\omega}\in\mb
    P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
    then \(\bmPoGame{\mb P}{W}\) is almost the Choquet game, except the first
    player also gets to choose a point. Note \(W\) is closed under zipping.
  \end{observation}

>>>>

  \section*{marks and tactics}

@@

  \section*{2+ marks and tactics}

  And this stuff is based on section 4.5.1 of \cite{bartoszynski1993covering}.

    % \begin{proposition}
    %   Suppose that for every finite collection \(\{\mb P_i:i<n\}\)
    %   such that \(\mb P=\bigcup_{i<n}\mb P_i\),
    %   some \(\mb P_i\) contains two incompatible points.
    %   Then \(\mb P\) contains an infinite antichain.
    % \end{proposition}
    %
    % \begin{proof}
    %   Suppose \(a_i\in\mb P_i\) have been defined for \(i<n\) such that
    %   \(a_i\not\in\bigcup_{j<i}\mb P_j\) and
    %   each \(\mb P_i\) is pairwise-compatible. It follows that
    %   \(\mb P\not=\bigcup_{i<n}\mb P_i\), so choose
    %   \(a_n\not\in\bigcup_{i<n}\mb P_i\) and let \(\mb P_n\) be a maximal family
    %   containing \(a_n\) such that \(\mb P_n\) is pairwise-compatible.
    %
    %   It follows that \(A=\{a_n:n<\omega\}\) is an antichain, since for
    %   every pair \(a_i,a_j\in A\) with \(i<j\), \(a_j\not\in\mb P_i\), so
    %   \(a_j\) is not compatible with something in \(\mb P_i\)...
    % \end{proof}

  \begin{definition}
    Let \(f\in S^{\leq\omega}\). Then \(f\rest n\in S^n\) is defined by
    \((f\rest n)(i)=f(i)\). (\(f\rest n\) gives the first \(n\) terms of \(f\).)

    Let \(t\in S^{<\omega}\). Then \(t\last k\in S^k\) is defined by
    \((t\last k)(i)=t(i+|t|-k)\). (\(t\last k\) gives the last \(n\) terms
    of \(t\).)
  \end{definition}

\begin{definition}
  For every partial order \(\mb P\) and compatible \(p,q\in\mb P\),
  let \(p\wedge q\) satisfy \(p\wedge q\leq p,q\).
\end{definition}

  \begin{claim}
    \(\mb P\) contains no infinite antichains if and only if every
    antichain in \(\mb P\) is of size \(n\) or less for some \(n<\omega\).
  \end{claim}

  \begin{proof}
    MAYBE? Apparently true for \(\mb P=\tau\setminus\{\emptyset\}\) due to
    Lemma 2.10 of \cite{comfort_negrepontis_1982}.
  \end{proof}

  \begin{proposition}
    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
    Suppose every antichain in \(\mb P\) is of size \(n<\omega\) or less,
    and \(\plII\win\bmPoGame{\mb P}{W}\). Then
    \(\plII\autowin\bmPoGame{\mb P}{W}\) (i.e. \(\plII\) wins every
    play of \(\bmPoGame{\mb P}{W}\), i.e. \(W=\mb P^\downarrow\)).
  \end{proposition}

  \begin{proof}
    First, let \(\{p_i:i<n\}\) be an antichain of size \(n<\omega\),
    then let \(\mb P_i\) be a maximal pairwise-compatible subset of \(\mb P\)
    containing \(p_i\). Note that if there existed
    \(q\in\mb P\setminus\bigcup_{i<n}\mb P_i\),
    \(q\) must be incompatible with some \(q_i\in\mb P_i\) for \(i<n\).
    Since \(p_i,q_i\in\mb P_i\), they are compatible, so let
    \(r_i=p_i\wedge q_i\). Since \(q\) is incompatible with \(q_i\) for \(i<n\),
    \(q\) is incompatible with \(r_i\) for \(i<n\). Since \(p_i\) is
    incompatible with \(p_j\) for \(i<j<n\), \(r_i\) is incompatible with
    \(r_j\) for \(i<j<n\). But that makes \(\{q\}\cup\{r_i:i<n\}\) an
    antichain of size \(n+1\), contradicting the assumption of the proposition.
    Thus \(\mb P=\bigcup_{i<n}\mb P_i\).

    We now show that if \(s\in\mb P_i^\downarrow\) for some \(i\),
    then \(s\in W\). Let \(\sigma\) be a
    winning strategy for \(\plII\) in \(\bmPoGame{\mb P}{W}\),
    and attack \(\sigma\) with \(q(0)=s(0)\wedge p_i\) and
    \(q(n+1)=s(n+1)\wedge\sigma(\<q(0),\dots,q(n)\>)\). Note that the choice
    of \(q(0)\) is valid as \(s(0),p_i\in\mb P_i\). Similarly,
    \(\sigma(\<q(0),\dots,q(n)\>)\leq q(0)\leq p_i\), so
    \(\sigma(\<q(0),\dots,q(n)\>)\) cannot be compatible with any \(p_j\)
    where \(j\not=i\). Thus \(s(n+1),\sigma(\<q(0),\dots,q(n)\>)\in\mb P_i\),
    making the choice of \(q(n+1)\) valid. Since \(\sigma\) is winning for
    \(\plII\), we see that \(q\in W\), and therefore \(s\in W\).

    Finally, consider any play of \(\bmPoGame{\mb P}{W}\). It must contain
    have a subsequence \(s\in\mb P_i^\downarrow\) for some \(i<n\),
    so \(s\in W\) and therefore
    the play is also in \(W\), securing a victory for \(\plII\).
  \end{proof}

  \begin{lemma}
    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
    Suppose that for every \(p\in\mb P\), there exists an infinite
    antichain \(A_p=\{a_p(n):n<\omega\}\subseteq\{q\in\mb P:q\leq p\}\).
    Then \(\plII\kmarkwin{(k+2)}\bmPoGame{\mb P}{W}\) if and only if
    \(\plII\ktactwin{(k+2)}\bmPoGame{\mb P}{W}\).
  \end{lemma}

  \begin{proof}
    Let \(\sigma\) witness \(\plII\kmarkwin{(k+2)}\bmPoGame{\mb P}{W}\).
    Define \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\) for \(t\in\mb P^1\).
    Since \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\leq a_{t(0)}(0)\leq t(0)\),
    this is a legal move.

    Consider \(t\in\mb P^{j+2}\) for \(j\leq k\).
    If there exists \(l_t<\omega\) such that
    \(t(j+1)\leq a_{t(j)}(l_t+j)\),
    define \(t'\in\mb P^{j+2}\) by \(t'(i)=a_{t(i)}(l_t+i)\) and let
    \(\tau(t)=\sigma(t',l_t+|t|)\). Note that since
    \[
      \tau(t)
        =
      \sigma(t',l_t+|t|)
        \leq
      t'(j+1)
        =
      a_{t(j+1)}(l_t+j+1)
        \leq
      t(j+1)
    \]
    this is a legal move. (If \(l_t\) failed to exist,
    we could arbitrarily let, say,
    \(\tau(t)=t(|t|-1)\); as we will see, this case will never occur
    for any legal attack against \(\tau\).)

    Let \(f\) be a legal attack against \(\tau\). The intuition of the
    following proof is simple: by construction, \(l_t\) will produce
    the number of \(\plI\)'s moves forgotten by \(\plII\)'s \((k+2)\)-tactic,
    allowing the \((k+2)\)-tactic to deduce the round number and thus exploit
    the winning \((k+2)\)-mark.

    We may quickly verify
    that \(l_{f\rest 2}=0\) since
    \[
      (f\rest 2)(1)
        =
      f(1)
        \leq
      \tau(f\rest 1)
        =
      \sigma(\<a_{f(0)}(0)\>,1)
        \leq
      a_{f(0)}(0)
        =
      a_{(f\rest 2)(0)}(0+0)
    .\]
    We claim in general that \(l_{f\rest(j+2)}=0\) for \(j\leq k\).
    Assuming \(l_{f\rest(j+2)}=0\) for \(j<k\),
    \[
      (f\rest(j+3))(j+2)
        =
      f(j+2)
        \leq
      \tau(f\rest(j+2))
        =
      \sigma(f\rest(j+2)',0+j+2)
        \leq
      f\rest(j+2)'(j+1)
    \]
    \[
        =
      a_{(f\rest(j+2))(j+1)}(j+1)
        =
      a_{(f\rest(j+3))(j+1)}(0+(j+1))
    \]
    proving \(l_{f\rest(j+3)}=0\).

    Now we show that \(l_{f\rest(j+2)\last(k+2)}=j-k\) for \(j\geq k\).
    We've just shown that this is true for our base case \(j=k\).
    Now assuming \(l_{f\rest(j+2)\last(k+2)}=j-k\), we show...
  \end{proof}
